Tabular Constraint Learning

### 2016-04-13 Paper/ECAI/tabular.tex
added the figure with insight

\subsection{Insights}

>>>>

\subsection{Insights}
We should explain Figure \ref{fig:fbi}, e.g. if we aggregate by the crime now, the missing value would not get into statistics, which seems faulty, since we can directly compute it.

\begin{figure*}[thb]
  \begin{center}
    \includegraphics[width=0.85\textwidth]{figures/fbi_figure_highlighted.png}
  \end{center}
  \caption{Real world tabular constraint reconstruction: FBI crime statistics}
  \label{fig:fbi}
\end{figure*}
